Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
forgotten file.

\subsection{Computations}

>>>>

\subsection{Computations}
%----------------------
Scaling results as a function of the number of processors, on the MIC and on the host. The host calculations
are performed for reference only, to bring out the dominance of the MIC due to its advanced swizzling and channel 
operations, not available on the host. The performance on the host is 3x slower than on the MIC. The large cache
of the host alleviates somewhat the lower memory bandwidth, but this only reduces the cost of transfer {\tt x}. 
The cost memory cost for {\tt A} and {\tt col\_id} is unaffected by the larger cache size.

The performance on the MIC scales linearly with the number of threads. We compare three cases, each with and without bandwidth reduction using Reverse Cuthil-McKee (RCM). There are $96^3$ RBF nodes, leading to a matrix with 884,736 rows. The four source vectors occupy more than 14M bytes, which exceeds the aggregate L2 cache of 31 Mbytes (7.8 Mfloats.)

\todo{Is the host architecture described? Problem: I had to change hosts a few weeks ago, and it has different characteristics}. 
%----------------------
